% 03/22 modified
%%%%%%%%%%%%%%%%%%%%%%%%
% References

%\addtolength{\baselineskip}{-1.0\baselineskip}
\begin{thebibliography}{99}
\end{thebibliography}

\begin{description}
 \item[] Abramowitz, M., and I.A. Stegun, ~(1972). ~{\it Handbook of Mathematical Functions}, ~Dover.
 \item[] Admati, A., and P. Pfleiderer, ~(1988). ~A theory of intraday patterns: volume and price variability, ~{\it Review of Financial Studies} 1, Spring, 3--40.
 \item[] Almgren, R., and N. Chriss, ~(1999).~Value under liquidation.~{\it Risk} 12(12),~61--63.
 \item[] Almgren, R., and N. Chriss, ~Optimal execution of portfolio transactions.~{\it Journal of Risk} 3(2), 5--39.
 \item[] Andersen, T.G., ~(1996). Return volatility and trading volume: an information flow interpretation of stochastic volatility, ~{\it Journal of Finance} 71, 169--204.
 \item[] Barclay, M. J., W.G. Christie, J. H. Harris, E. Kandel, and P. H. Schultz,~(1999).~The effects of market reform on the trading costs and depths of Nasdaq stocks.~{\it Journal of Finance} 54, 1--34.
 \item[] BARRA.~(1997).~{\it Market Impact Model Handbook}.
 \item[] Bellman, R.~(1997).~{\it Introduction to Matrix Analysis}, SIAM.
 \item[] Bertsimas, D., and A. Lo, ~(1998). ~Optimal control of execution costs, ~{\it Journal of Financial Markets} 1, 1--50.
 \item[] Biais, B., P. Hillion, and C. Spatt, ~(1995).~An empirical analysis of the limit order book and the order flow in the Paris bourse.~{\it Journal of Finance} 50, 1655--1689.
 \item[] Black, F., and R. Litterman, ~(1991).~Asset allocation: combining investor views  with market equilibrium.~{\it Journal of Fixed Income} 1(2), ~7--18.
 \item[] Chakravarty, S., and C. Holden, ~(1995). An integrated model of market and limit orders, ~{\it Journal of Financial Intermediation} 4, 213--241.
 \item[] Chan, K.C., W.G. Christie, and P.H. Schultz, ~(1995). Market structure and the intraday pattern of bid-Ask Spreads for NASDAQ securities, ~{\it Journal of Business} 68, 35--60.
 \item[] Clark, P.K., ~(1973). A subordinated stochastic process model with finite variance for speculative prices, ~{\it Econometrica} 41, 135--155.
 \item[] Collins, B., and F. Fabozzi, ~(1991).~A methodology for measuring transaction costs.~{\it Financial Analysts Journal} 47, 27--36.
 \item[] Copeland, T.~C., and D. Galai, ~(1983).~Information effects on the bid-ask spread.~{\it Journal of Financial Economics} 7, 229--263.
 \item[] Epps, T.W., and M.L. Epps, ~(1976). The Stochastic dependence of security price changes and transaction volumes: implications for the mixture-of-distributions hypothesis, ~{\it Econometrica} 44, 305--321.
 \item[] Foster, D., and S. Viswanathan, ~(1990). A theory of the interday variations in volume, variance, and trading costs in securities markets, ~{\it Review of Financial Studies} 3, 593--624.
 \item[] Grinold, R., and R. Kahn, ~(1999).~{\it Active Portfolio Management}.~McGraw-Hill Professional Publishing.
 \item[] Hausman, J., A. Lo, and C. MacKinlay, ~(1992). ~An orderd probit analysis of transaction stock prices, ~{\it Journal of Financial Economics} 31, 319--379.
 \item[] Harris, L., and J. Hasbrouck, ~(1996). Market vs. limit orders: the SuperDOT evidence on order submission strategy, ~{\it Journal of Financial and Quantitative Analysis} 31, 213--231.
 \item[] Holthausen, R., R. Leftwich, and D. Mayers, ~(1987).~The effect of large block transactions on security prices: a cross-sectional analysis.~{\it Journal of Financial Economics} 19, 237--268.
 \item[] Hisata, Y., and Y. Yamai, ~(2000).~An analysis on practical liquidity risk measurement.  Institute for Monetary and Economic Studies Discussion Paper 2000-J-3.
 \item[] Jain, P.C., and G. Joh,  ~(1988).~The dependence between hourly
	    prices and trading volume.~{\it Journal of Financial Quantitative Analysis} 23, 269--283.
 \item[] Jorion, P., ~(2000).~{\it Value at Risk}.~McGraw-Hill.
 \item[] Karpoff, J.M., ~(1987). The relation between price changes and trading volume: a survey, ~{\it Journal of Financial and Quantitative Analysis} 22, 109--126.
 \item[] Kawahara, J., ~(1994).  ~Evaluation of execution cost and best execution
 (in Japanese), ~{\it Security Analysts Journal} 12, 32--47.
 \item[] Kawahara, J., and Y. Murase, ~(1993).~Analysis on intraday stock price
 movement.~(in Japanese) {\it Security Analysts Journal} 11, 10--21.
 \item[] Kolmogorov, A.N., and S.V. Fomin, ~(1970).~{\it Introductory Real Analysis}.~Dover.
 \item[] Konishi, H., ~(2002). ~Optimal slice of a VWAP trade, ~{\it Journal of Financial Markets} 5(2) 197--221.
 \item[] Konishi, H., and N. Makimoto, ~(2001). ~Optimal slice of a block trade, ~{\it Journal of Risk} 3(4), 33--51.
 \item[] Konno, H., and A. Wijayanayake,  ~(1998). ~A mean-absolute deviation portfolio optimization model under transaction costs.  Dept. of IE and Management, Tokyo Institute of Technology.
 \item[] Kyle, A. S., ~(1985).~Continuous auctions and insider trading.~{\it  Econometrica} 53, 1315--1335.
 \item[] Lehman, B.N., and D. M. Modest,   ~(1994).~Trading and liquidity on the Tokyo Stock Exchange: a bird's eye view.~{\it  Journal of Finance} 49, 951--984.
 \item[] Mannen, S., and J. Uno, ~(2000).~Basket orders and basis costs.~(in Japanese) {\it NQI Report} 3, 19--22.
 \item[] Markovitz, H., ~(1959). ~{\it Portfolio Selection: Efficient Diversification of Investments}. ~John Wiley \& Sons, Inc.
 \item[] McInish, T. H., and R. A. Wood,  ~(1991).~An analysis of intraday patterns in bid/ask spreads for NYSE stocks. Working Paper, Memphis State University.
 \item[] Parlour, C. A., ~(1998).~Price dynamics in limit order markets.~{\it Review of Financial Studies} 11, 789--816.
 \item[] Perold, A., ~(1988).~The implementation shortfall: paper versus reality.~{\it Journal of Portfolio Management} 14, ~4--9.
 \item[] Protter, P. E., ~(1990). ~{\it Stochastic Integration and Differential Equations: A New Approach}. ~Springer Verlag.
 \item[] Ross, S. A., ~(1976).~The arbitrage theory of capital asset pricing.~{\it Journal of Economic Theory} 13, ~341--360.
 \item[] Sharpe, W., ~(1970). ~{\it Portfolio Theory and Capital Market}. ~McGraw-Hill.
 \item[] Subrahmanyam, A., ~(1991).~Risk aversion, market liquidity, and price efficiency.~{\it Review of Financial Studies} 4(3), 417--442. 
 \item[] Tauchen, G.E., and M. Pitts, ~(1983). The price variability-volume relationship on speculative markets, ~{\it Econometrica} 51, 485--505.
 \item[] Uno, J., and M. Yamada, ~(1993).~Empirical study on market impact.~(in Japanese) {\it Security Analysts Journal} 11, 22--34.
\end{description}
